Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-06-08 analysis/sim/run_simpw.Rmd
more sims

SIMS=500
#run 500 sims
FRAC_DE=0.05
FC=1
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,1.1,1.2,1.3,1.4,1.5)

@@

dev.off()

>>>>

SIMS=1000
#run 500 sims
FRAC_DE=0.05
FC=1
N_REPS=3
DGE_FUNC="deseq2"
SUM_COUNT=2e7
VARIANCE=c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,1.1,1.2,1.3,1.4,1.5)

@@

plot(cp$VARIANCE,cp$p,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="precision")
points(fo$VARIANCE,fo$p,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$p,type="b",pch=19,col="blue")
grid()
legend("bottomleft", inset=.02, title="tool",
   c("clusterprofiler","fora","fgsea"), col=c("black","red","blue"),
   horiz=FALSE, cex=1.2, pch=19,lwd=2)

plot(cp$VARIANCE,cp$r,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="recall")
points(fo$VARIANCE,fo$r,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$r,type="b",pch=19,col="blue")
grid()
plot(cp$VARIANCE,cp$f,ylim=c(0,1),type="b",pch=19,xlab="variance added",ylab="index",main="f1")
points(fo$VARIANCE,fo$f,type="b",pch=19,col="red")
points(fg$VARIANCE,fg$f,type="b",pch=19,col="blue")
grid()
dev.off()
